```{r setup, include=FALSE}

# Initial set-up, libraries
library(flexdashboard)
library(eem)
library(ggplot2)
library(highcharter)
library(quantmod)
library(dplyr)
library(treemap)
library(tidyquant)

# dates
d1 <- "201706" # latest available month
d2 <- "201606" # same month, a year earlier

d2_real <- "2017-07-01" # one month after latest available month

#### ----------------------- Loading some functions, to download data! 
source("functions.R")
token_inegi <- "502ae69d-a835-8bd5-0e73-2173cc35c83d"

### Dowloading data!
options(timeout = 500)
dld <- getComtradeData(months = c(d1, d2))
ndata <- dld$data

### To review data and see if all countries have data
# ndata %>% group_by(yr, rtTitle, ptTitle, rgDesc) %>% summarise("n" = n()) %>% View(.)

# level 2 category names
l2 <- read.table(file = "https://raw.githubusercontent.com/Eflores89/proyectos/master/data/tradewatch/l2-code-names.txt", 
                 sep = "|", header = T, 
                 colClasses = c("character","character"))
# level 4
l4 <- read.table(file = "https://raw.githubusercontent.com/Eflores89/proyectos/master/data/tradewatch/l4-code-names.txt", 
                 sep = "|", header = T, 
                 colClasses = c("character","character"))
cutoff <- 1000000

# data %>% group_by(period, rtCode, ptCode, rgDesc) %>% summarise("n" = n()) %>% View(.)



### Download inegi data
exports <- inegiR::series_exportaciones_pais(token = token_inegi)

mxn_exp_usa <- exports[, 1:2]
names(mxn_exp_usa) <- c("Dates", "Exports")
mxn_exp_usa <- mxn_exp_usa %>% dplyr::filter(Dates<d2_real)
mxn_exp_usa <- as_xts(mxn_exp_usa, date_col = Dates)

mxn_exp_can <- exports[, c(1,3)]
names(mxn_exp_can) <- c("Dates", "Exports")
mxn_exp_can <- mxn_exp_can %>% dplyr::filter(Dates<d2_real)
mxn_exp_can <- as_xts(mxn_exp_can, date_col = Dates)

can_imports <- inegiR::serie_inegi(serie = "http://www3.inegi.org.mx/sistemas/api/indicadores/v1//Indicador/133428/00000/es/false/xml/", 
                                   token = token_inegi)
can_imports <- as_xts(can_imports, date_col = Fechas)

usa_imports <- inegiR::serie_inegi(serie = "http://www3.inegi.org.mx/sistemas/api/indicadores/v1//Indicador/133429/00000/es/false/xml/", 
                                   token = token_inegi)
usa_imports <- as_xts(usa_imports, date_col = Fechas)

```


Mexico - US Trade {data-orientation=columns, data-navmenu="Bilateral Trade"}
=====================================


Column {data-width=600}
-----------------------------------------------------------------------

### Mexico to USA export matrix

```{r}
summarise_df(data = ndata, name2 = l2, name4 = l4, from = "mx", to = "usa", type = "exports", threshold = cutoff)
```

> HS 4-Level Codes with a smaller trade value than 1 million usd dollars in latest month are grouped and labeled as "smaller". Source: UN Comtrade.


### Total Mexican exports to USA

```{r}
hchart(mxn_exp_usa) %>% hc_add_theme(hc_theme_eem) %>% hc_navigator(enabled = FALSE)
```

> Source: INEGI.

Column {data-width=600}
-----------------------------------------------------------------------


### Mexico from USA import matrix

```{r}
summarise_df(data = ndata, name2 = l2, name4 = l4, from = "mx", to = "usa", type = "import", threshold = cutoff)
```

> HS 4-Level Codes with a smaller trade value than 1 million usd dollars in latest month are grouped and labeled as "smaller". Source: UN Comtrade.

### Total Mexican imports from USA

```{r}
hchart(usa_imports) %>% hc_add_theme(hc_theme_eem) %>% hc_navigator(enabled = FALSE)
```

> Source: INEGI.


Mexico - Canada Trade {data-orientation=columns, data-navmenu="Bilateral Trade"}
=====================================

Column {data-width=600}
-----------------------------------------------------------------------

### Mexico to Canada export matrix

```{r}
summarise_df(data = ndata, name2 = l2, name4 = l4, from = "mx", to = "can", type = "exports", threshold = cutoff)
```

> HS 4-Level Codes with a smaller trade value than 1 million usd dollars in latest month are grouped and labeled as "smaller". Source: UN Comtrade.

### Total Mexican exports to Canada

```{r}
hchart(mxn_exp_can) %>% hc_add_theme(hc_theme_eem) %>% hc_navigator(enabled = FALSE)
```

> Source: INEGI.


Column {data-width=600} 
-----------------------------------------------------------------------


### Mexico from Canada import matrix

```{r}
summarise_df(data = ndata, name2 = l2, name4 = l4, from = "mx", to = "can", type = "import", threshold = cutoff)
```

> HS 4-Level Codes with a smaller trade value than 1 million usd dollars in latest month are grouped and labeled as "smaller". Source: UN Comtrade.

### Total Mexican imports from Canada

```{r}
hchart(can_imports) %>% hc_add_theme(hc_theme_eem) %>% hc_navigator(enabled = FALSE)
```

> Source: INEGI.


US Share-Shift {data-orientation=columns}
=====================================


### Changes of share of Mexican products in U.S. Market

```{r}
summarise_mkt(data = ndata, name2 = l2, name4 = l4, mkt = "usa", pivot = "mx", threshold = cutoff)
```


> Imports are not collectively exhaustive (the U.S. market is represented by only the two other NAFTA countries). Source: UN Comtrade.



Terms of Trade & Fx {data-orientation=columns}
=====================================


Column {data-width=600} 
-----------------------------------------------------------------------

### MXN-USD Exchange Rate

```{r}
usdmxn <- as_xts(tidyquant::tq_get("DEXMXUS", get = "economic.data"), date_col = date)
hchart(usdmxn) %>% hc_add_theme(hc_theme_eem) %>% hc_navigator(enabled = FALSE)
```

> Source: Federal Reserve Bank of St. Louis.

### USD Trade-weighted exchange rate

```{r}
twusd <- as_xts(tidyquant::tq_get("TWEXB", get = "economic.data"), date_col = date)
hchart(twusd) %>% hc_add_theme(hc_theme_eem) %>% hc_navigator(enabled = FALSE)
```

> Broad measure. Source: Federal Reserve Bank of St. Louis.

Column {data-width=400} 
-----------------------------------------------------------------------

### Mexican Import Price Index

```{r}
mxprice <- as_xts(tidyquant::tq_get("MEXTOT", get = "economic.data"), date_col = date)
hchart(mxprice) %>% hc_add_theme(hc_theme_eem) %>% hc_navigator(enabled = FALSE)
```

> Source: Federal Reserve Bank of St. Louis.

### Canada Import Price Index

```{r}
canprice <- as_xts(tidyquant::tq_get("CANTOT", get = "economic.data"), date_col = date)
hchart(canprice) %>% hc_add_theme(hc_theme_eem) %>% hc_navigator(enabled = FALSE)
```

> Source: Federal Reserve Bank of St. Louis.

